\documentclass[a4paper]{article}
\setlength\parindent{0pt}

\usepackage{amsthm, amsmath, amssymb, verbatim, enumerate, mathtools,
algorithm, pgfplots}
\usepackage{rotating}
\usepackage[margin=0.5in]{geometry}
\usetikzlibrary{arrows, quotes}

\begin{document}

Relation Web
\begin{itemize}
    \item Let $D$ be the set of descriptors.
    \item Let $R$ be the set of possible relations.
    \item Let $G = \left( V, E \right)$ be a directed graph where $V = D$ and
        $E$ is a set of edges such that each $v \in V$ has $|R| \times |D|$
        edges, one per relation per descriptor (exhaustively listing all 
        possible relations between this descriptor and all other descriptors).
    \item Goal: assign each edge $e \in E$ a weight $P(e) \in [0, 1]$ that
        represents the probability of that being a valid relation.
    \item Idea: as triples are processed, adjust the weight of not only the 
        ``explicit'' relation between the relevant descriptors that is directly
        stated with that triple, but also the ``implicit'' relation(s).
        % Knowledge graph?
\end{itemize}<++>

Probability Representation
\begin{itemize}
    \item Let the set $R$ contain all the relations between all possible
        relations between all descriptors. 
    \item Sample Space: Assign each $r \in R$ a value $0, 1$ indicating whether
        or not that relation is valid. Let $S$ be the space of all such
        outcomes.
    \item Let $T$ be the set of all training triples.
    \item Want to find: $s \in S$ such that $P(s | T)$ is maximized.
    \item Assume perfect relation extraction from triples.
    \item Let $R_E$ be the set of all explicit relations extracted from $T$.
    \item Let $R_I$ be the set of all explicit relations extracted from $R_E$.
\end{itemize}

Rudimentary Algorithm
\begin{itemize}
%    \item Assumptions:
%    \begin{itemize}
%        \item Triple classification is perfect.
%    \end{itemize}
    \item Explicit relation detection:
    \begin{itemize}
        \item For each triple, label the detected explicit relations with their
            probabilities.
    \end{itemize}
    \item Drawing implications:
    \begin{itemize}
        \item For every pair of descriptors $A, B$ find all non-zero paths $A
            \rightarrow B$. Store these paths and their vertex labels and edge
            probabilites in a data structure indexed by descriptor pair.
        \item ``Collate'' the entries for every pair of descriptors of the same
            respective labels, finding clusters of paths that tend to be
            correlated with one another.
    \end{itemize}<++>
\end{itemize}<++>

%\begin{tikzpicture}
%
%\tikzset{vertex/.style = {shape=circle,draw,minimum size=1.5em}}
%\tikzset{edge/.style = {->,> = latex'}}
%% vertices
%\node[vertex] (A) at  (0,5) {$A$};
%\node[vertex] (X) at  (0,0) {$X$};
%\node[vertex] (B) at  (5,0) {$B$};
%%edges
%%\draw[edge] (A) to[bend left=50] (X) node [midway, fill=white] {1} ;
%%\draw[edge] (A) to["2", bend left] (X);
%%\draw[edge] (X) to["1", bend right=10] (A);
%%\draw[edge] (X) to["2", bend left=10] (A);
%%\draw[edge] (A) to["1", bend right] (B);
%%\draw[edge] (A) to["2", bend left] (B);
%%\draw[edge] (B) to["1", bend right=10] (A);
%%\draw[edge] (B) to["2", bend left=10] (A);
%%\draw[edge] (B) to["1", bend right] (X);
%%\draw[edge] (B) to["2", bend left] (X);
%%\draw[edge] (X) to["1", bend right=10] (B);
%%\draw[edge] (X) to["2", bend left=10] (B);
%
%\end{tikzpicture}
\end{document}
